Output Summary

### 2023-06-02 03-post-process/output-plots-children/03-fit-to-data.Rmd
Implement empty_plot()

#### Spring Smolt $\rightarrow$ LGR (NOR)

@@

#### Spring Smolt $\rightarrow$ LGR (HOR)

```{r spring-surv-fit-hor, fig.width = p4_width, fig.height = p4_height}
# function to create the plot for one population
plot_f = function(j) {
  plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_hor, pop = j)),
               obs = get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]),
               label_text = pops[j], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
}

@@

```{r min-weir-ss, fig.width = 5, fig.height = 2.5}
weir_sample_size(j_min)
```

>>>>

#### Spring Smolt $\rightarrow$ LGR {.tabset .tabset-pills}

##### NOR

@@

##### HOR

```{r spring-surv-fit-hor, fig.width = p4_width, fig.height = p4_height}
# function to create the plot for one population
plot_f = function(j) {
  if (j != j_min) {
    plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_hor, pop = j)),
               obs = get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]),
               label_text = pops[j], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
  } else {
    empty_plot(label_text = pops[j])
  }

@@

```{r min-weir-ss, fig.width = 5, fig.height = 2.5}
mypar(mfrow = c(1,1), mar = c(1,1,1,1), oma = c(0,0,0,0))
empty_plot(text = "No Weir Data")
```

### 2023-06-02 03-post-process/output-plots-children/08-misc-processes.Rmd
Implement empty_plot()

```{r phi-O0-O1-hor-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  keep = sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = c(0, 0.4))
}

@@

```{r phi-O1-O2-hor-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  keep = sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
}

@@

```{r phi-O2-O3-hor-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  keep = sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
}

@@

```{r psi-O1-hor-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  keep = sub_index("^psi_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = c(0, 0.4))
}

@@

```{r psi-O2-hor-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  keep = sub_index("^psi_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
}

@@

```{r n-stray, fig.width = p4_width, fig.height = p4_height}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("^G[year,origin,pop]", pop = j, year = ts_yrs, origin = o_hor)), yrs = all_yrs[ts_yrs], label_text = pops[j])
}

@@

```{r stray-comp, fig.width = p4_width, fig.height = p4_height}
plot_fn = function(j) {
  x = post_summ(post, sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = j))

  mp = barplot(x["mean",], ylim = ylim_01, xaxt = "n", col = tran_cols["model"], border = main_cols["model"])
  segments(mp, x["2.5%",], mp, x["97.5%",], col = alpha("red", 0.5))
  axis(side = 1, at = mp, labels = paste0("Age", jags_data$kmin:jags_data$kmax), las = 1)
  segments(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[3], xpd = TRUE, col = par("col.axis"))
  segments(par("usr")[1], par("usr")[3], par("usr")[1], par("usr")[4], xpd = TRUE, col = par("col.axis"))
  panel_label(pops[j])
}

mypar()
junk = sapply(1:jags_data$nj, plot_fn)
axis_labels("Age of Return", "Proportion of Strays by Age")
```

>>>>

```{r phi-O0-O1-hor-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  if (j != j_min) {
    keep = sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
    plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = c(0, 0.4))
  } else {
    empty_plot(label_text = pops[j])
  }
}

@@

```{r phi-O1-O2-hor-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  if (j != j_min) {
    keep = sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
    plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
  } else {
    empty_plot(label_text = pops[j])
  }
}

@@

```{r phi-O2-O3-hor-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  if (j != j_min) {
    keep = sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
    plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
  } else {
    empty_plot(label_text = pops[j])
  }
}

@@

```{r psi-O1-hor-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  if (j != j_min) {
    keep = sub_index("^psi_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
    plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = c(0, 0.4))
  } else {
    empty_plot(label_text = pops[j])
  }
}

@@

```{r psi-O2-hor-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  if (j != j_min) {
    keep = sub_index("^psi_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
    plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
  } else {
    empty_plot(label_text = pops[j])
  }
}

@@

```{r n-stray, fig.width = p4_width, fig.height = p4_height}
plot_fn = function(j) {
  if (length(simulated) > 0 & j != j_min) {
    empty_plot(label_text = pops[j])
  } else {
    plot_tseries(est = post_summ(post, sub_index("^G[year,origin,pop]", pop = j, year = ts_yrs, origin = o_hor)), yrs = all_yrs[ts_yrs], label_text = pops[j])
  }
}

@@

```{r stray-comp, fig.width = p4_width, fig.height = p4_height}
plot_fn = function(j) {

  if (length(simulated) > 0 & j != j_min) {
    empty_plot(label_text = pops[j])
  } else {
    x = post_summ(post, sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = j))
    mp = barplot(x["mean",], ylim = ylim_01, xaxt = "n", col = tran_cols["model"], border = main_cols["model"])
    segments(mp, x["2.5%",], mp, x["97.5%",], col = alpha("red", 0.5))
    axis(side = 1, at = mp, labels = paste0("Age", jags_data$kmin:jags_data$kmax), las = 1)
    segments(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[3], xpd = TRUE, col = par("col.axis"))
    segments(par("usr")[1], par("usr")[3], par("usr")[1], par("usr")[4], xpd = TRUE, col = par("col.axis"))
    panel_label(pops[j])
  }
}

mypar()
junk = sapply(1:jags_data$nj, plot_fn)
axis_labels("Age of Return", "Age Composition of Strays")
```
